Appendix

### 2021-07-06 manuscript/appendix.Rmd
:pen:

```{r}
# compare over grid set of candidate r and K
rs <- c(0.01, 0.1, 0.2, 0.3, 0.4, 0.5, 2)
Ks <- c(0.5, 1, 1.5, 4, 10, 16)
sigma <- 0.1
n_models <- length(rs)*length(Ks)
pars <- expand.grid(rs, Ks)
names(pars) <- c("r", "K")
pars$sigma <- 0.1
closure <- function(r, K){
  function(x, h = 0){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
  }
}
many_models <-  lapply(1:n_models, function(i) closure(pars[i,"r"], pars[i,"K"]))

>>>>

```{r}
# compare over grid set of candidate r and K
rs <- seq(.1, 2, length=6)
Ks <- seq(1,19,by=3)
sigma <- 0.1
n_models <- length(rs)*length(Ks)
pars <- expand.grid(rs, Ks)
names(pars) <- c("r", "K")
pars$sigma <- 0.1
closure <- function(r, K){
  function(x, h = 0){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
  }
}
many_models <-  lapply(1:n_models, function(i) closure(pars[i,"r"], pars[i,"K"]))
